Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-03-10 main.tex
minor: commented keywords back in

%    \begin{IEEEkeywords}
%        DAG, Heterogeneous platform, Adaptive scheduling, Memory constraint.
%    \end{IEEEkeywords}

@@

%%% CONTEXT %%%
The analysis of massive datasets, originating from fields such as genomics, 
remote sensing, or biomedical imaging -- to name just a few -- has become ubiquitous in science;
this often takes the form of workflows, \iec separate software components chained together
in some kind of complex pipeline~\cite{DBLP:journals/dbsk/LeserHDEGHKKKKK21}.
These workflows are usually represented as directed acyclic graphs (DAGs).
The DAG vertices represent the software components (or, more generally, the workflow \emph{tasks}),
while the edges model I/O dependencies between the tasks~\cite{adhikari2019survey,liu2018survey}.
Large workflows with resource-intensive tasks can easily exceed the capabilities of a 
single computer and are therefore executed on a parallel or distributed platform.
An efficient execution of the workflows on such platforms requires the mapping of tasks
to specific processors.
\new{A task schedule - \iec a valid execution order that respects the dependencies,  and possibly also starting times for
the tasks are needed to increase utilization by reusing finished processors.}

@@

%%% CONTRIBUTION %%%
%\paragraph*{Contribution} 
The main contributions of this paper are both algorithmic and experimental:
\begin{itemize}
\item We formalize the problem with memory constraints, where communication buffers
are used to evict data from memory if it will be later used by another processor. 
\item We design three HEFT-based heuristics
that adhere to memory size constraints: \heftbl, \heftblc, and \heftmm.
M behind HEFT \new{stands for} for \underline{m}emory, BL for \underline{b}ottom \underline{l}evel,
BLC for \underline{b}ottom \underline{l}evel with \underline{c}ommunication, 
and MM for \underline{m}inimum \underline{m}emory traversal.
The difference between the new heuristics is the way they prioritize tasks for processor assignment.

@@

Marchal~et~al.~\cite{marchal2018parallel} assume a memory model where each processor has an individual memory available.
Workflow tasks have no memory requirements, but they have input and output files that need to be stored in the memory.
A polynomial-time algorithm for computing the peak memory needed for a parallel execution of such a workflow DAG is provided,
as well as an integer linear programming (ILP) solution to the scheduling problem.
The memory model \new{requires deleting all input files when the task starts and adding all output files to memory.}

Other models consider for instance a 
%In an assumed 
dual-memory system~\cite{herrmann2014memory} where a processor can have access 
to two different kinds of memory, and each task can be executed on only one sort of memory.
%Communication happens only between these two kinds of processors (communication within 
%each group is ignored).
The authors then present an ILP-based solution for this problem formulation.
%
%The algorithm presented by Yao et al.
Yao et al.~\cite{yao2022memory} consider that each processor has its own internal memory, and all
processors share a common external one. The internal (local) memory is used to store the task files.
The external memory is used to store evicted files to make room for the execution of a task on a processor.
%All processors, including the original one, can access these files. 
%Each edge %in~\cite{yao2022memory} 
%has two weights -- the size of the files transferred along it,
%and the time of communication along this edge.
%The tasks themselves have no memory requirements, but need to hold all their incoming and outgoing files.
%
In~\cite{ding2024ils}, the authors consider connected processors with individual limited memories
forming a global memory, with different access times to memory, and no weights on edges. An ILP
is proposed in this setting. 
%The collective set of memories forms the global memory to which each processor has access;
%however, the access time to global memory is different.
%Each memory access in the graph is modeled as a memory access token on the task, while the edges have no weights.
%The solved problem is how to allocate the initial input data in processor memories so that the overall
%execution is minimized and the memories are not exceeded.
%To this end, the authors propose an ILP model.
%%that minimizes the length of the critical path, including a greedy initial solution.
%
%In~\cite{rodriguez2019exploration}, the authors assume memory requirements on tasks represented as tiles.
%Each processor has individual memories to process the task, but only the shared memories store the tiles containing
%memory tiles occupied by memory tiles.
%
There are also some cloud-oriented models that include costs associated with memory usage~\cite{liang2020memory}.

Overall, there are a variety of memory models, but, to the best of our knowledge, the only study on a multiprocessor
platform that is fully heterogeneous, with individual memories, is the one from~\cite{DBLP:conf/icpp/KulaginaMB24}.
Yet, they propose only a partitioning-based mapping of the workflow, without processor reuse.
\new{Because a processor is idle after a partition of a workflow has finished executing}, in~\cite{DBLP:conf/icpp/KulaginaMB24},
there is no need for communication buffers to store data
that should be \new{exchanged} between two processors when tasks are ready to execute.

@@

    Garg~\etal~\cite{GARG2015256} propose a dynamic scheduling algorithm for heterogeneous grids based on rescheduling.
    The procedure involves building a first (static) schedule with HEFT, periodic resource monitoring, 
    and rescheduling the remaining tasks. 
%    The resource model contains resource groups (small tightly-connected sub-clusters), connected between each other.
%    For each resource group, there is an own scheduler, and an overall global scheduler responsible for distributing
%    tasks to groups.
%    The static heuristic is HEFT with earliest start time as priority.
    Upon rescheduling, a new mapping is calculated from scratch, and this mapping is accepted if the resulting makespan
    is smaller than the previous one.
%    The experiments were conducted on a single workflow with 10 tasks.
%
    % The authors define the execution time, estimated start time, data ready time,a dn estimated finish time per task.
    %The runtimes of tasks depend on processor speeds, are calculated in advance and stored in tables.

@@

    De Olivera~\etal~\cite{de2012provenance} propose a tri-criteria (makespan, reliability, cost) adaptive scheduling algorithm
    for clouds.
    They solve a set of linear equations that represent the cost of an execution based on the criteria.
    The authors test four scenarios -- one preferring each criterion and a balanced one.
    The algorithm chooses the best virtual machine for each next task based on the cost given by the model.
    The authors used workflows with less than ten tasks, but repeated them so that the execution had up to 200 tasks.
    %They do not report the runtime of the scheduling algorithm, only the speedup and cost saving it produces.
 %   The authors use provenance data to make scheduling decisions.

    Daniels \etal~\cite{daniels1995robust} formalize the concept of robust scheduling with variable processing times
    on a single machine.
    The changes in runtimes of tasks are not due to changing machine properties, but are rather task-related
    and thus unrelated to each other.
    The authors search for an optimal schedule
%    formulate a decision space of all permutations of $n$ jobs, and the optimal schedule 
    in relation to a performance measure. % $\phi$.
    Then they proceed to formulate the Absolute Deviation Robust Scheduling Problem as a set of linear constraints.

While several related works consider building a new schedule once some variation has been observed,
we are not aware of work implementing a real runtime system that interacts with the scheduler
and has been tested on workflows with thousands of tasks, as we propose in this paper. Furthermore, 
we are not aware of any previous work discussing dynamic algorithms combined with memory constraints. 
%\AB{Say why our approach in dynamic setting is different and novel}

@@

\begin{table}[b]
    \begin{center}
        \begin{tabular}{c|c|cc}
            \toprule
            Processor  %& Amount
            &  CPU speed   & \multicolumn{2}{c}{Memory size (GB)} \\
            name & (GHz) & {\em default} & {\em mem-constrained} \\
            \midrule
            local                    & 4                    & 16     & 1.6 \\
            A1                      & 32                   & 32     & 3.2 \\
            A2                      & 6                    & 64    & 6.4 \\
            N1                      & 12                   & 16     & 1.6 \\
            N2                      & 8                    & 8      & 0.8\\
            C2                      & 32                   & 192   &  19.2\\
            \bottomrule
        \end{tabular}
    \end{center}
    \caption{Cluster configurations.}
    \label{tab:procs}
\end{table}

@@

\subsubsection{Runtime system}
\label{ss:runtime-sys}
%
To simulate the execution of a workflow, we implemented a runtime system.
It reads the historical data and builds weights for tasks as explained above.
%    These weights are then treated as the ``truth'' about the execution during the simulation.
In the static case, these values are being sent to the scheduler, which builds a schedule
according to these weights.
In the dynamic setting, in turn, the runtime system applies a deviation function to the values.
This function computes a normally distributed random deviation value, where the initial value
is the mean and the deviation is~$10\%$.
This scenario corresponds to the real-life scenarios identified in Ref.~\cite{lotaru} and
other works dedicated to predicting task running times~\cite{da2015online,da2013toward}.

@@

\begin{figure}[tb]
  \centering
  \includegraphics[width=1.08\columnwidth] {images/success-rates-large2}
  \vspace{-0.8cm}
  \caption{Success rates \new{by workflow size and algorithm} on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
  \vspace{-0.15cm}
\end{figure}

We also report in  Figure~\ref{fig:ms-relations-by-workflow} the relative makespan found
by the memory-aware heuristics, normalized to the
makespan achieved by \heft, often with an invalid over-optimistic schedule that exceeds
the bound on memory.
%    Figure~\ref{fig:ms-relations-by-workflow} shows the relations of the makespans found by the heuristics to the
%    makespans found by the baseline (including invalid ones), by workflow size.
\new{The makespans found by \heftbl are $<13\%$ worse than those found by the baseline for workflows with less than \numprint{2000}
tasks, and up to $27\%$ worse for the largest workflows.
The makespans of \heftblc are very similar,being $<17\%$ worse on smallest workflows, $19$-$28\%$ worse on middle-sized,
and up to $30\%$ worse on the largest workflows.
The makespans found by \heftmm are $25$-$30\%$ worse on the smallest workflows, $40$-$70\%$ on middle-sized and up to
$210\%$ on the largest ones. These are still very encouraging results,
in particular for \heftbl and \heftblc, since the makespans of \heft correspond to invalid schedules.
}
 %   \skug{TODO: how much worse are makespans for SUCCESSFUL hefts? presulmably almost identical}

@@

\begin{figure}[tb]
    \centering
  \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size_barplot}
    \vspace{-0.8cm}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal2}
    \vspace{-0.6cm}
    \caption{Memory usage on default cluster, including invalid \heft schedules. }
%by algorithm by workflow size
     \label{fig:mem-usages-normal}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal-onlyvalid2}
    \vspace{-0.6cm}
    \caption{Memory usage on default cluster, considering only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
    \vspace{-0.15cm}
\end{figure}

\subsubsection{Scheduling on the memory-constrained cluster}
\label{ss:mem-constrained-cluster}
%
On the memory-constrained cluster, \heft produces valid assignments in only $14$ out of $290$ experiments
$290$~($4.8\%$ success rate).
The successful schedules are achieved exclusively on the tiny workflows (with only two 200-task size-increased
workflow among them).
\heftbl successfully schedules $38\%$ of the workflows, \heftblc is able to schedule $49\%$ of them, while \heftmm
still schedules all of them, including even the largest ones, see Figure~\ref{fig:success-rates-tiny}.
As also observed on the default cluster, \heftmm seems to be less affected by the workflow size
than the other heuristics.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/success-rates-tiny}
    \caption{Success rates on the memory-constrained cluster. Higher is better. }
%        by algorithm by workflow size.
    \label{fig:success-rates-tiny}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size-constrained-barplot}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-constrained-onlyvalid2}
    \caption{Memory usage on the memory-constrained  cluster. } % by different heuristics by workflow size.}
    \label{fig:memory-usage-constrained}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm \new{in case of no recomputation}. Smaller is better.}
    \label{fig:updates-ms}
    \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/runtimes-logarithmic2}
    \caption{Average running times (in seconds) of the heuristics \wrt workflow size. The $y$-axis is logarithmic.}
    \label{fig:runtimes-log}
    \vspace{-0.3cm}
\end{figure}

@@

>>>>

    \begin{IEEEkeywords}
        DAG, Heterogeneous platform, Adaptive scheduling, Memory constraint.
    \end{IEEEkeywords}

@@

%%% CONTEXT %%%
The analysis of massive datasets, originating from fields such as genomics, 
remote sensing, or biomedical imaging -- to name just a few -- has become ubiquitous in science;
this often takes the form of workflows, \iec separate software components chained together
in some kind of complex pipeline~\cite{DBLP:journals/dbsk/LeserHDEGHKKKKK21}.
These workflows are usually represented as directed acyclic graphs (DAGs).
The DAG vertices represent the software components (or, more generally, the workflow \emph{tasks}),
while the edges model I/O dependencies between the tasks~\cite{adhikari2019survey,liu2018survey}.
Large workflows with resource-intensive tasks can easily exceed the capabilities of a 
single computer and are therefore executed on a parallel or distributed platform.
An efficient execution of the workflows on such platforms requires the mapping of tasks
to specific processors.
\new{Moreover, a task schedule -- \iec a valid execution order that respects the dependencies --
and possibly also starting times for the tasks are needed to increase utilization by reusing 
processors that have become idle after finishing a task.}

@@

%%% CONTRIBUTION %%%
%\paragraph*{Contribution} 
The main contributions of this paper are both algorithmic and experimental:
\begin{itemize}
\item We formalize the problem with memory constraints, where communication buffers
are used to evict data from memory if it will be later used by another processor. 
\item We design three HEFT-based heuristics
that adhere to memory size constraints: \heftbl, \heftblc, and \heftmm.
M behind HEFT stands for \underline{m}emory, BL for \underline{b}ottom \underline{l}evel,
BLC for \underline{b}ottom \underline{l}evel with \underline{c}ommunication, 
and MM for \underline{m}inimum \underline{m}emory traversal.
The difference between the new heuristics is the way they prioritize tasks for processor assignment.

@@

Marchal~et~al.~\cite{marchal2018parallel} assume a memory model where each processor has an individual memory available.
\new{Workflow tasks themselves have no memory requirements for their computations,
but they have input and output files that need to be stored in the memory.}
A polynomial-time algorithm for computing the peak memory needed for a parallel execution of such a workflow DAG is provided,
as well as an integer linear programming (ILP) solution to the scheduling problem.
The memory model \new{requires deleting all input files when the task starts and adding all output files to memory.}

Other models consider for instance a 
%In an assumed 
dual-memory system~\cite{herrmann2014memory} where a processor can have access 
to two different kinds of memory, and each task can be executed on only one sort of memory.
%Communication happens only between these two kinds of processors (communication within 
%each group is ignored).
The authors then present an ILP-based solution for this problem formulation.
%
%The algorithm presented by Yao et al.
Yao et al.~\cite{yao2022memory} consider that each processor has its own internal memory, and all
processors share a common external one. The internal (local) memory is used to store the task files.
The external memory is used to store evicted files to make room for the execution of a task on a processor.
%All processors, including the original one, can access these files. 
%Each edge %in~\cite{yao2022memory} 
%has two weights -- the size of the files transferred along it,
%and the time of communication along this edge.
%The tasks themselves have no memory requirements, but need to hold all their incoming and outgoing files.
%
Ding \etal~\cite{ding2024ils}, in turn, consider connected processors with individual limited memories
forming a global memory, with different access times to memory and no weights on edges. An ILP
is proposed in this setting. 
%The collective set of memories forms the global memory to which each processor has access;
%however, the access time to global memory is different.
%Each memory access in the graph is modeled as a memory access token on the task, while the edges have no weights.
%The solved problem is how to allocate the initial input data in processor memories so that the overall
%execution is minimized and the memories are not exceeded.
%To this end, the authors propose an ILP model.
%%that minimizes the length of the critical path, including a greedy initial solution.
%
%In~\cite{rodriguez2019exploration}, the authors assume memory requirements on tasks represented as tiles.
%Each processor has individual memories to process the task, but only the shared memories store the tiles containing
%memory tiles occupied by memory tiles.
%
There are also some cloud-oriented models that include costs associated with memory usage~\cite{liang2020memory}.

Overall, there are a variety of memory models, but, to the best of our knowledge, the only study on a multiprocessor
platform that is fully heterogeneous, with individual memories, \new{is our own previous work~\cite{DBLP:conf/icpp/KulaginaMB24}.}
\new{Yet, in that paper we only propose} a partitioning-based mapping of the workflow, without processor reuse.
\new{Since a processor is idle after a workflow partition has finished its execution,
there is no need in Ref.~\cite{DBLP:conf/icpp/KulaginaMB24} for communication buffers to store data
that should be \new{exchanged} between processors when tasks are ready to execute.}

@@

    Garg~\etal~\cite{GARG2015256} propose a dynamic scheduling algorithm for heterogeneous grids based on rescheduling.
    The procedure involves building a first (static) schedule with HEFT, periodic resource monitoring, 
    and rescheduling the remaining tasks. 
%    The resource model contains resource groups (small tightly-connected sub-clusters), connected between each other.
%    For each resource group, there is an own scheduler, and an overall global scheduler responsible for distributing
%    tasks to groups.
%    The static heuristic is HEFT with earliest start time as priority.
    Upon rescheduling, a new mapping is calculated from scratch, and this mapping is accepted if the resulting makespan
    is smaller than the previous one.
    \todo[inline]{Maybe mention: from scratch computation because of tiny workflows??}
%    The experiments were conducted on a single workflow with 10 tasks.
%
    % The authors define the execution time, estimated start time, data ready time,a dn estimated finish time per task.
    %The runtimes of tasks depend on processor speeds, are calculated in advance and stored in tables.

@@

De Olivera~\etal~\cite{de2012provenance} propose a tri-criteria (makespan, reliability, cost) adaptive scheduling algorithm
for clouds.
They solve a set of linear equations\todo{Mis\-lea\-ding, TBD!} that represent the cost of an execution based on the criteria.
The authors test four scenarios -- one preferring each criterion and a balanced one.
The algorithm chooses the best virtual machine for each next task based on the cost given by the model.
The authors use workflows with less than ten tasks, but repeat them so that the execution has up to 200 tasks.
%They do not report the runtime of the scheduling algorithm, only the speedup and cost saving it produces.
%   The authors use provenance data to make scheduling decisions.

Daniels \etal~\cite{daniels1995robust} formalize the concept of robust scheduling with variable processing times
on a single machine.
The changes in task running times are not due to changing machine properties, but are rather task-related
and thus unrelated to each other.
The authors search for an optimal schedule
%    formulate a decision space of all permutations of $n$ jobs, and the optimal schedule 
in relation to a performance measure. % $\phi$.
Then they proceed to formulate the Absolute Deviation Robust Scheduling Problem \new{with} a set of linear constraints.

While several related works consider building a new schedule once some variation has been observed,
we are not aware of work implementing a real runtime system that interacts with the scheduler
and has been tested on workflows with thousands of tasks, as we propose in this paper. Furthermore, 
we are not aware of any previous work discussing dynamic algorithms combined with memory constraints.

@@

\begin{table}[tb]
    \begin{center}
        \begin{tabular}{c|c|cc}
            \toprule
            Processor  %& Amount
            &  CPU speed   & \multicolumn{2}{c}{Memory size (GB)} \\
            name & (GHz) & {\em default} & {\em mem-constrained} \\
            \midrule
            local                    & 4                    & 16     & 1.6 \\
            A1                      & 32                   & 32     & 3.2 \\
            A2                      & 6                    & 64    & 6.4 \\
            N1                      & 12                   & 16     & 1.6 \\
            N2                      & 8                    & 8      & 0.8\\
            C2                      & 32                   & 192   &  19.2\\
            \bottomrule
        \end{tabular}
    \end{center}
    \caption{Cluster configurations.}
    \label{tab:procs}
\end{table}

@@

\subsubsection{Runtime system}
\label{ss:runtime-sys}
%
To simulate the execution of a workflow, we implemented a runtime system.
It reads the historical data and builds weights for tasks as explained above.
%    These weights are then treated as the ``truth'' about the execution during the simulation.
In the static case, these values are being sent to the scheduler, which builds a schedule
according to these weights.
In the dynamic setting, in turn, the runtime system applies a deviation function to the values.
This function computes a normally distributed random deviation value, where the initial value
is the mean and the deviation is~$10\%$.
This scenario corresponds to the real-world scenarios identified in Ref.~\cite{lotaru} and
other works dedicated to predicting task running times~\cite{da2015online,da2013toward}.

@@

\begin{figure}[tb]
  \centering
  \includegraphics[width=1.0\columnwidth] {images/success-rates-large2}
%  \vspace{-0.8cm}
  \caption{Success rates by workflow size and algorithm on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
%  \vspace{-0.15cm}
\end{figure}

We also report in  Figure~\ref{fig:ms-relations-by-workflow} the relative makespan found
by the memory-aware heuristics, normalized to the
makespan achieved by \heft, \new{the latter} often with an invalid over-optimistic schedule that exceeds
the memory bound.
%    Figure~\ref{fig:ms-relations-by-workflow} shows the relations of the makespans found by the heuristics to the
%    makespans found by the baseline (including invalid ones), by workflow size.
\new{The makespans found by \heftbl are $<13\%$ worse than those found by the baseline for workflows with less than \numprint{2000}
tasks, and up to $27\%$ worse for the largest workflows.
The makespans of \heftblc are very similar, being $<17\%$ worse on smallest workflows, $19$-$28\%$ worse on middle-sized,
and up to $30\%$ worse on the largest workflows.
The makespans found by \heftmm are $25$-$30\%$ worse on the smallest workflows, $40$-$70\%$ on middle-sized and up to
$210\%$ on the largest ones.} These are still very encouraging results,
in particular for \heftbl and \heftblc, since the makespans of \heft\ \new{often} correspond to invalid schedules.

 %   \skug{TODO: how much worse are makespans for SUCCESSFUL hefts? presulmably almost identical}

@@

\begin{figure}[tb]
    \centering
  \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size_barplot}
%    \vspace{-0.8cm}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
%    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal2}
%    \vspace{-0.6cm}
    \caption{Memory usage on default cluster, including invalid \heft schedules. }
%by algorithm by workflow size
     \label{fig:mem-usages-normal}
%    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal-onlyvalid2}
%    \vspace{-0.6cm}
    \caption{Memory usage on default cluster, considering only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
%    \vspace{-0.15cm}
\end{figure}

\subsubsection{Scheduling on the memory-constrained cluster}
\label{ss:mem-constrained-cluster}
%
On the memory-constrained cluster, \heft produces valid assignments in only $14$ out of $290$ experiments ($4.8\%$ success rate).
The successful schedules are achieved exclusively on the tiny workflows (with only two 200-task size-increased
workflow among them).
\heftbl successfully schedules $38\%$ of the workflows, \heftblc is able to schedule $49\%$ of them, while \heftmm
still schedules all of them, including even the largest ones, see Figure~\ref{fig:success-rates-tiny}.
As also observed on the default cluster, \heftmm seems to be less affected by the workflow size
than the other heuristics.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/success-rates-tiny}
    \caption{Success rates on the memory-constrained cluster. Higher is better. }
%        by algorithm by workflow size.
    \label{fig:success-rates-tiny}
%    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size-constrained-barplot}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
%    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-constrained-onlyvalid2}
    \caption{Memory usage on the memory-constrained  cluster. } % by different heuristics by workflow size.}
    \label{fig:memory-usage-constrained}
%    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm \new{in case of no recomputation}. Smaller is better.}
    \label{fig:updates-ms}
%    \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/runtimes-logarithmic2}
    \caption{Average running times (in seconds) of the heuristics \wrt workflow size. The $y$-axis is logarithmic.}
    \label{fig:runtimes-log}
%    \vspace{-0.3cm}
\end{figure}

@@

\medskip
